\section{Downloads}

After users view and filter the results, they may want to download information for use offline.
Each download should be a single zipped file, which contains only plain text files with a logical directory/folder structure.

%--------------------------------------------------
\subsection{Obtaining testing files}
\label{sec:downloads_element}
%--------------------------------------------------

When an \Element is downloaded, the user should receive:
\begin{itemize}
    \item Information about it (\cref{sec:tables_element}), written in an auto-generated text file.
    \item \Tree files and/or generating script and information (\cref{sec:tables_tree}).
    \item If applicable, \Trait files and/or generating script and information (\cref{sec:tables_trait}).
\end{itemize}
These files should all have sensible names.

When multiple \Elements are downloaded together, each should be in a separate directory.
If they have tree or trait files in common, could have an option to use symlinks instead of duplicating the content.
Also, a spreadsheet (CSV file, one row per \Element) should be included so it's easy to see which \Elements have which attributes (columns in \Tree, membership in \Refset, \etc).

If an entire \Refset is requested for download, each \Element within it should be in a separate directory.

If an entire \Benchmark is requested for download, each \Refset within it should be in a separate directory.

Need to decide on the file format for \Tree and \Trait.
Some options:
\begin{itemize}
    \item One Nexus file per \Element, containing all the trees and all the traits.  Uncluttered, but more annoying to parse.
    \item One file per \Tree (each line a Newick string) and one file per \Trait (CSV with one column per trait).
    \item One file per tree (many per \Tree) and one file per trait (many per \Trait), with filenames that show which belong together (\eg \texttt{t001.tre} and \texttt{s001.csv}).
\end{itemize}

% todo: link to view to access this

%--------------------------------------------------
\subsection{Obtaining methods scripts}
\label{sec:downloads_method}
%--------------------------------------------------

When a \Method is downloaded, the user should receive:
\begin{itemize}
    \item Information about it, written in an auto-generated text file.
    \item The script to run it.
\end{itemize}

When multiple \Methods are downloaded together, each should be in a separate directory.

% todo: link to view to access this

%--------------------------------------------------
\subsection{Obtaining performance reports}
\label{sec:downloads_report}
%--------------------------------------------------

The user should be able to download a CSV file that looks basically like the results table \Report (\cref{sec:views_report_task} or \cref{sec:views_report_method}).
Either the full report could be requested, or only to include those rows (\Elements) and columns that are visible after interacting with the report view.

Are additional columns needed, \eg directory names of \Elements and \Methods if they are downloaded?
