\section{Users}

Different kinds of users will interact with \phycomb in different ways.
They will have different goals and permissions.
One person could be a different type of user at different times, \eg I could do some work as an Administrator, then add data as a Contributor, than look through results as a Viewer.

%--------------------------------------------------
\subsection{Viewer}
%--------------------------------------------------

Can browse \phycomb contents through the web interface.
Cannot make changes that affect anyone else.
No login required.

%--------------------------------------------------
\subsection{Contributor}
%--------------------------------------------------
\label{sec:users_contributor}

All the functionality of a Viewer.
Additionally, Contributors can see and use the parts of the web interface for uploading \Elements, \Methods, and \Performance.
Login required.

Should the newly uploaded material be immediately integrated into the database and visible to all users, or should it not be published until an Administrator approves the submission?

Contributors can't delete information, but perhaps they could flag \Elements, \etc that are no longer useful, so an Administrator could delete them.

%--------------------------------------------------
\subsection{Administrator}
%--------------------------------------------------

Can approve the uploads and suggested deletions made by Contributors.
Can also make changes to the structure (\eg which \Elements are in a \Benchmark).
Perhaps the interface will be different than what a Viewer or Contributor sees.
Login required.
